### 2023-04-25 paper.Rmd
this is better

When defining a new variable $y = (y_1, \ldots, y_N)$ as the squared deviation of each observation from the mean $\overline{\mathbf{x}}$, the sample variance of $x$ can be reformulated as the mean of $y$:

$$
y_i = (x_i - \overline{\mathbf{x}})^2
$$

>>>>

When defining a new variable $y = (y_1, \ldots, y_N)$ as the squared deviation of each observation from the mean $\overline{\mathbf{x}}$, i.e. $y_i = (x_i - \overline{\mathbf{x}})^2$, the sample variance of $x$ can be reformulated as the mean of $y$:
